Freezing of a Weeks-Chandler-Anderson Fluid using Classical Density Functional Theory

### 2020-12-15 papers/thesis-kirstie/thesis.tex

While models for particular fluids were being created, powerful methods 
to describe the properties of fluids were also being developed. 
In the late 1950s, Scaled Particle Theory (SPT)~\cite{ReissSPT} was 
introduced from which an equation of state, and an expression for the 
excess Helmholtz free energy of a homogeneous hard-sphere fluid can be 
obtained~\cite{Hansen}. 
%\textcolor{red}{
In 1958, Percus-Yevick introduced an alternative method 
for the hard-sphere fluid based on an approximate closure to the 
Ornstein-Zernike integral equation~\cite{PercusYevick}.
%Percus and Yevick took another approach to the hard-sphere fluid.
In 1961 Morita and Hiroike introduced a density functional 
approach~\cite{MoritaDFT} to finding the equilibrium Grand and Helmholtz free energies, 
and the corresponding equilibrium number density profile for 
inhomogeneous fluids. To use this classical Density Functional Theory (cDFT) 
approach, an expression for the free energy 
as a functional of an average number density that varies spatially 
must be constructed for a particular fluid.
%DFT Evans 1979
%Led by the consistency between results from SPT and Percus-Yevick, 
In 1989 Rosenfeld introduced Fundamental Measure Theory (FMT)~\cite{rosenfeld1989,rosenfeld1988} 
to form a functional for the hard-sphere fluid based on the idea that 
the lowest term in the virial expansion 
of the excess chemical potential for a hard-sphere fluid can 
be expressed in terms of a sum of weighted densities using a weight 
function of the form of a backward Heavyside step function (shown below) 
that can be expressed in terms of a sum of convolutions involving 
a set of weight functions related to the geometry of a sphere.
\begin{displaymath}
   \theta(|\vec r - \vec r'|-(\vec R_i + \vec R_j)) = w_i^{(3)} \otimes w_j^{(0)} + w_j^{(3)} \otimes w_i^{(0)} + w_i^{(1)} \otimes w_j^{(2)} + w_j^{(1)} \otimes w_i^{(2)}\end{displaymath}
\begin{equation}   + \vec w_i^{(1)} \otimes \vec w_j^{(2)} + \vec w_j^{(1)} \otimes \vec w_i^{(2)}
\end{equation}
FMT gives the same result for the excess Helmholtz free energy of the hard-sphere fluid as 
SPT does, from which it can be constructed~\cite{rosenfeld1989,Hansen,santos2012phi3},
and for the direct correlation function approximation given by Percus-Yevick.
Tarazona later improved on the 
method by introducing a tensor version of one of the energy density terms 
in the functional~\cite{tarazonaphi3, 
santos2012phi3}, and in 1999 Schmidt adopted FMT for spheres with soft 
interatomic potential energies
(which rise to infinity over a distance, rather than instantaneously 
like the potential energy between hard spheres)
forming Soft Fundamental Measure Theory (SFMT)\cite{schmidt1999density}.

@@

>>>>

While models for particular fluids were being created, powerful methods 
to describe the properties of fluids were also being developed. 
In the late 1950s, Scaled Particle Theory (SPT)~\cite{ReissSPT} was 
introduced from which an equation of state, and an expression for the 
excess Helmholtz free energy of a homogeneous hard-sphere fluid can be 
obtained~\cite{Hansen}. 
%\textcolor{red}{
In 1958, Percus-Yevick introduced an alternative method 
for the hard-sphere fluid based on an approximate closure to the 
Ornstein-Zernike integral equation~\cite{PercusYevick}.
%Percus and Yevick took another approach to the hard-sphere fluid.
In 1961 Morita and Hiroike introduced a density functional 
approach~\cite{MoritaDFT} to finding the equilibrium Grand and Helmholtz free energies, 
and the corresponding equilibrium number density profile for 
inhomogeneous fluids. To use the classical Density Functional Theory (cDFT) 
approach, an expression for the free energy 
as a functional of an average number density that varies spatially 
must be constructed for a particular fluid.
%DFT Evans 1979
%Led by the consistency between results from SPT and Percus-Yevick, 
In 1989 Rosenfeld introduced Fundamental Measure Theory (FMT)~\cite{rosenfeld1989,rosenfeld1988} 
to form a functional for the hard-sphere fluid based on the idea that 
the lowest term in the virial expansion 
of the excess chemical potential for a hard-sphere fluid can 
be expressed in terms of a sum of weighted densities using a weight 
function of the form of a backward Heavyside step function (shown below) 
that can be expressed in terms of a sum of convolutions involving 
a set of weight functions related to the geometry of a sphere.
\begin{displaymath}
   \theta(|\vec r - \vec r'|-(\vec R_i + \vec R_j)) = w_i^{(3)} \otimes w_j^{(0)} + w_j^{(3)} \otimes w_i^{(0)} + w_i^{(1)} \otimes w_j^{(2)} + w_j^{(1)} \otimes w_i^{(2)}\end{displaymath}
\begin{equation}   + \vec w_i^{(1)} \otimes \vec w_j^{(2)} + \vec w_j^{(1)} \otimes \vec w_i^{(2)}
\end{equation}
FMT gives the same result for the excess Helmholtz free energy of the hard-sphere fluid as 
SPT does, from which it can be constructed~\cite{rosenfeld1989,Hansen,santos2012phi3},
and for the direct correlation function approximation given by Percus-Yevick.
Tarazona later improved on the 
method by introducing a tensor version of one of the energy density terms 
in the functional~\cite{tarazonaphi3, 
santos2012phi3}, and in 1999 Schmidt adopted FMT for spheres with soft 
interatomic potential energies
(which rise to infinity over a distance, rather than instantaneously 
like the potential energy between hard spheres)
forming Soft Fundamental Measure Theory (SFMT)\cite{schmidt1999density}.

@@

%\begin{figure}
  %\centering
  %%\includegraphics[height=8cm]{figs/w2-w3-radius-thickness.png}
  %%\caption{}
  %\label{fig:weight_functions}
%\end{figure}

%\begin{figure}
  %\centering
  %%\includegraphics[height=8cm]{figs/df-dr_withXi_fromB2.pdf}
  %%\caption{}
%\end{figure}

%\begin{figure}
  %\centering
  %%\includegraphics[height=8cm]{figs/erf_Potential_overkT-xifromB2.pdf}
  %%\caption{}
%\end{figure}

%\begin{figure}
  %\centering
  %%\includegraphics[height=8cm]{figs/B2_vs_T_with_xi_fromB2.pdf}
  %%\caption{}
%\end{figure}
